Staged Abstract Interpreters

### 2018-11-17 paper/50_cases.tex
revise

\citeauthor{Boucher:1996:ACN:647473.727587} introduced abstract compilation (AC) as a new
implementation technique for abstract interpretation based static analysis \cite{Boucher:1996:ACN:647473.727587}.
The idea is inspired by partial evaluation similar to the present paper -- the program can be known 
statically therefore the overhead of interpretation can be eliminated. 
In AC, the compiled analysis can be represented by either text or closures (higher-order functions);
the closures can be executed immediately however the textual program need to be compiled and loaded first.

Specifically, \citeauthor{Boucher:1996:ACN:647473.727587} show how to compile a monovariant control-flow 
analysis \cite{Shivers:1991:SSC:115865.115884, Shivers:1988:CFA:53990.54007} 
for continuation-passing style (CPS) programs. Since the analyzed program is written in CPS, the analyzer 
is essentially a big-step control-environment abstract interpreter.
Closure generation compiles the analysis as a closure which takes an environment as argument.
The overhead of traversing the abstract syntax tree of input program also has been eliminated.

>>>>

\citeauthor{Boucher:1996:ACN:647473.727587} introduced abstract compilation (AC) as a new
implementation technique for abstract interpretation based static analysis \cite{Boucher:1996:ACN:647473.727587}.
The idea is inspired by partial evaluation similar to the present paper -- the program can be known 
statically, the overhead of interpretation can be eliminated. 
In AC, the compiled analysis can be represented by either text or closures (higher-order functions);
though the closures can be executed immediately, the textual programs need to be compiled and loaded first.

Specifically, \citeauthor{Boucher:1996:ACN:647473.727587} show how to compile a monovariant control-flow 
analysis \cite{Shivers:1991:SSC:115865.115884, Shivers:1988:CFA:53990.54007} 
for continuation-passing style (CPS) programs. Since the analyzed program is written in CPS, the analyzer 
is essentially a big-step control-environment abstract interpreter.
Closure generation compiles the analysis as a closure taking an environment argument.
The overhead of traversing the abstract syntax tree of input program also has been eliminated.

### 2018-11-17 paper/60_eval.tex
revise

Our evaluations shows that the staged abstract interpreter performs well in some
cases that are considered to be the worst scenarios for traditional $k$-CFA.
The staged version outperforms the unstaged abstract interpreter by a significant
margin (up to ~230\% performance gain) on these difficult ones.

>>>>

Our evaluations show that the staged abstract interpreter performs well in some
cases that are considered to be the worst scenarios for traditional $k$-CFA.
The staged version outperforms the unstaged abstract interpreter by a significant
margin (up to ~230\% performance gain) on these difficult ones.
